Using the simodels package with different input classes

### 2022-06-13 data-raw/si-classes.Rmd
Update name again, close #20 again

---
title: "Using the si package with different input classes"
output: github_document
---

@@

```{r setup}
# remotes::install_github("robinlovelace/si")
library(si)
# ?si_predict
```

>>>>

---
title: "Using the simodels package with different input classes"
output: github_document
---

@@

```{r setup}
# remotes::install_github("robinlovelace/simodels")
library(simodels)
# ?si_predict
```

### 2022-06-13 data-raw/sim-paper.Rmd
Update name again, close #20 again

---
# title: "sim: A Package for Developing Spatial Interaction Models"
# output: rmarkdown::html_vignette
# vignette: >
#   %\VignetteIndexEntry{sim: A Package for Developing Spatial Interaction Models}
#   %\VignetteEngine{knitr::rmarkdown}
#   %\VignetteEncoding{UTF-8}

@@

output: rticles::jss_article
documentclass: jss
author:
  - name: FirstName LastName
    orcid: 0000-0000-0000-0000
    affiliation: University/Company
    # use this syntax to add text on several lines
    address: |
      | First line
      | Second line
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Second Author
    orcid: 0000-0000-0000-0000
    affiliation: 'Affiliation \AND'
    # To add another line, use \AND at the end of the previous one as above
  - name: Third Author
    orcid: 0000-0000-0000-0000
    address: |
      | Department of Statistics and Mathematics,
      | Faculty of Biosciences,
      | Universitat Autònoma de Barcelona
    affiliation: |
      | Universitat Autònoma
      | de Barcelona
    # use a different affiliation in adress field (differently formated here)
    affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "\\pkg{sim}: A Package for Developing Spatial Interaction Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "sim: A Package for Developing Spatial Interaction Models"
  # For running headers, if needed
  short:     "\\pkg{sim}: Spatial Interaction Models"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial interaction, movement, "\\proglang{R}"]
  plain:     [spatial interaction, movement, R]
preamble: >
  \usepackage{amsmath}
---

>>>>

---
# title: "simodels: A Package for Developing Spatial Interaction Models"
# output: rmarkdown::html_vignette
# vignette: >
#   %\VignetteIndexEntry{simodels: A Package for Developing Spatial Interaction Models}
#   %\VignetteEngine{knitr::rmarkdown}
#   %\VignetteEncoding{UTF-8}

@@

output: rticles::jss_article
documentclass: jss
author:
  - name: FirstName LastName
    orcid: 0000-0000-0000-0000
    affiliation: University/Company
    # use this syntax to add text on several lines
    address: |
      | First line
      | Second line
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Second Author
    orcid: 0000-0000-0000-0000
    affiliation: 'Affiliation \AND'
    # To add another line, use \AND at the end of the previous one as above
  - name: Third Author
    orcid: 0000-0000-0000-0000
    address: |
      | Department of Statistics and Mathematics,
      | Faculty of Biosciences,
      | Universitat Autònoma de Barcelona
    affiliation: |
      | Universitat Autònoma
      | de Barcelona
    # use a different affiliation in adress field (differently formated here)
    affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "\\pkg{simodels}: A Package for Developing Spatial Interaction Models"
  # If you use tex in the formatted title, also supply version without
  plain:     "simodels: A Package for Developing Spatial Interaction Models"
  # For running headers, if needed
  short:     "\\pkg{simodels}: Spatial Interaction Models"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial interaction, movement, "\\proglang{R}"]
  plain:     [spatial interaction, movement, R]
preamble: >
  \usepackage{amsmath}
---
